Refinements for open automata

### 2023-03-09 2021-Refinement/paper/refinementarticleV2.tex
proofs small things

 Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have, for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  {\wedge \reach{A_{13}}\mpar{s_{13}}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}

@@

The proof of the rest of the formula follows the same steps as the previous case the only argument that change is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and $g_{23x}  \Leftrightarrow g_{2x}$ and the actions of $\alpha_{13}$ and $\alpha_{23x}$ are renaming of  $\alpha_{1}$ and $\alpha_{2x}$ resp. The same for $\beta_{13j}$ and $\beta_{23xj}$ that are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.

\TODO{Redone! To check}

@@

 Furthermore, by hypothesis we have  \(A_1\subst{A_2}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have, for all $t_{12} \in T_{12}$:
\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]

>>>>

 Furthermore,  according to the Definition \ref{Def:Reach} (reachability applied to the composed automaton ${A_1\subst{A_3}{k}}$) we have, for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  {\wedge \reach{A_{13}}\mpar{s_{13}}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}

@@

The proof of the rest of the formula follows the same steps as the previous case the only argument that change is that by composition we obtain:  $g_{13} $ is the same as $ g_1$ and $g_{23x}$  is the same as $g_{2x}$ and the actions of $\alpha_{13}$, resp. $\alpha_{23x}$, is the same as  $\alpha_{1}$, resp. $\alpha_{2x}$. Similarly $\beta_{13j}$ and $\beta_{23xj}$ that are the same as $\beta_{1j}$ and $\beta_{2xj}$ respectively.
 We also apply the reachability definition but only on the automaton $A_1$

@@

 Furthermore, according to the Definition \ref{Def:Reach} (reachability, applied to the composed automaton \(A_1\subst{A_2}{k}\)) we have, for all $t_{12} \in T_{12}$:
\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]
